Stochastic modeling of EGS using continuum-fracture approach and multilevel Monte Carlo

### 2019-07-18 paper.tex
Change notation of open part l to L.

Number of wells: 2 \\
Depth: 5 km \\
Distance: 200 m \\
Well radius: $\rho = 15$ cm \\
Length of open part of wells: $l=60$ m \\

@@

{\bf The test geometry:}The wells are connected by three fractures, two of them intersecting the cylinders and one intersecting the first two fractures.

\subsection{Analytical models in the vicinity of the wells}
In order to keep mesh size treatable, we replace the Dirichlet boundary condition for the pressure applied on the open part of the well by the Robin type condition:
%
\eq{\label{eq:H_robin} k\nabla H\cdot\nn = \sigma(H-H_w), }
%
applied on the cut-out cylinders of the radii $R=10$ m. We assume the constant conductivity $k$ in the vicinity of wells. The parameter $\sigma$ is determined from the analytical radially symmetric solution
of the steady Darcy flow problem with a point source:
\[
    h(r) = -\alpha \log (r) + \beta
\]
where $r$ is the distance from the well and $\alpha$, $\beta$ are arbitrary constants.
The flux through the cylinder of the radius $r$ and the length $L$ is the constant
\[  
    Q = -2\pi \rho L k h'(\rho) = 2\pi L k \alpha,
\]
where we have used the Darcy law with the conductivity $k$. Now we use the analytical solution to fit the Robin type boundary condition:
\[
    Q = 2\pi R l \sigma (h(\rho) - h(R)) = 2\pi R l \sigma \alpha \log(R/\rho),
\]
which combined with previous equality determines $\sigma$ as:
\[ 
    \sigma = \frac{k}{R\log(R/\rho)}.
\]

>>>>

Number of wells: 2 \\
Depth: 5 km \\
Distance: 200 m \\
Well radius: $\rho = 15$ cm \\
Length of open part of wells: $L=60$ m \\

@@

{\bf The test geometry:} The wells are connected by three fractures, two of them intersecting the cylinders and one intersecting the first two fractures.

\subsection{Analytical models in the vicinity of the wells}
In order to keep mesh size treatable, we replace the Dirichlet boundary condition for the pressure applied on the open part of the well by the Robin type condition:
%
\eq{\label{eq:H_robin} k\nabla H\cdot\nn = \sigma(H-H_w), }
%
applied on the cut-out cylinders of the radii $R=10$ m. We assume the constant conductivity $k$ in the vicinity of wells. The parameter $\sigma$ is determined from the analytical radially symmetric solution
of the steady Darcy flow problem with a point source:
\[
    h(r) = -\alpha \log (r) + \beta
\]
where $r$ is the distance from the well and $\alpha$, $\beta$ are arbitrary constants.
The flux through the cylinder of the radius $r$ and the length $L$ is the constant
\[  
    Q = -2\pi \rho L k h'(\rho) = 2\pi L k \alpha,
\]
where we have used the Darcy law with the conductivity $k$. Now we use the analytical solution to fit the Robin type boundary condition:
\[
    Q = 2\pi R L \sigma (h(\rho) - h(R)) = 2\pi R L \sigma \alpha \log(R/\rho),
\]
which combined with previous equality determines $\sigma$ as:
\[ 
    \sigma = \frac{k}{R\log(R/\rho)}.
\]
